Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
white space

    These evolution models also provide a first estimate of the companions other properties such as \(T_{\textrm{eff}}\), logg, \(R/R_{\sun}\) and the magnitude in many other wavelength bands.  The companion \(T_{\textrm{eff}}\) and logg values specifically were utilized to influence the selection of synthetic model grids to perform the \(\chi^2\) analysis over in Section~\ref{sec:results}.

>>>>

    These evolution models also provide a first estimate of the companions other properties such as \(T_{\textrm{eff}}\), logg, \(\textrm{R/R}_{\sun}\) and the magnitude in many other wavelength bands.  The companion \(T_{\textrm{eff}}\) and logg values specifically were utilized to influence the selection of synthetic model grids to perform the \(\chi^2\) analysis over in Section~\ref{sec:results}.
